Bootstrap Confidence Intervals for Regression Discontinuity Designs with Uniform Kernels

### 2016-02-24 main_paper.tex
Couple of typos.

Note that the procedure as presented here only works for the uniform kernel, sharp RD designs, and i.i.d. data. Extensions to other kernels, higher order discontinuities, cross-sectional dependence, and the fuzzy RD design is the subject of ongoing research.

>>>>

Note that the procedure as presented here only coversr the uniform kernel, sharp RD designs, and i.i.d. data. Extensions to other kernels, higher order discontinuities, cross-sectional dependence, and the fuzzy RD design are subject of ongoing research.
